\ttitle

### 2015-08-26 Chapters/Discussion.tex
Discussion - Mo Comments

\clearpage
%----------------------------------------------------------------------------------------
\section{Summary of Aims}

@@

@@

The results presented in chapter \ref{ch_cpet_outcomes} demonstrated that cardiopulmonary exercise testing has a role in identifying high risk patients who are more likely to develop complications, stay longer in hospital and are less likely to receive adjuvant therapy after pancreaticoduodenectomy. 
These findings have since been replicated by other authors examining the role of cardiopulmonary exercise testing in pancreatic surgery.

@@

The results of our work in chapter \ref{ch_cpet_outcomes} as well as that of several others over the past 2 decades support the use of cardiopulmonary exercise testing as a clinical risk assessment tool in patients undergoing major surgery.

@@

%################################################################################
\subsection{Obstructive jaundice}
%################################################################################
In our opinion, the most important observation made in chapter \ref{ch_cpet_jaundice} was the lack of association between obstructive jaundice and poor cardiopulmonary function. 
We are aware of only one other similar study by Junejo and co-workers. They reported that peripheral oxygen extraction was normal during cardiopulmonary exercise in patients with malignant obstructive jaundice.\parencite{junejo_peripheral_2014} 
Preoperative biliary drainage is unlikely to improve aerobic fitness or modify their cardiopulmonary response to exercise/surgery \parencite{parker_serum_2014}.

@@

In their, appropriately titled paper \textit{`The Quandary of Preresection Biliary Drainage for Pancreatic Cancer'}, the authors discuss the complex physiological effects of obstructive jaundice, its impact on immune function and the differences between findings in animal studies and humans \parencite{tol_quandary_2012}.
However, they also review recent literature where there appears to be overwhelming evidence that preoperative biliary drainage increases the incidence of postoperative complications, especially infective complications. \parencite{van_der_gaag_preoperative_2010, arkadopoulos_preoperative_2014, fujii_preoperative_2015, furukawa_negative_2015}.

In chapter \ref{ch_outcomes} we reported that obstructive jaundice was not associated with increased incidence of postoperative complications or prolonged hospital stay. 
Taken together, our results support the emerging view that routine preoperative biliary drainage should no longer be performed in all patients scheduled to undergo a pancreaticoduodenectomy.

@@

Our results suggest that poor performance at cardiopulmonary exercise testing may not necessarily be related to only cardiac or pulmonary function. 
Body composition appears to not only affect aerobic capacity but also systemic inflammation.
Improvements in body composition in cancer patients are achievable through nutritional supplementation \parencite{machado_whey_2015} as well as increased physical activity.
Improvement in our understanding of cancer cachexia and the role of inflammation will also help optimise patients for treatment and prolong survival.

>>>>

\clearpage
%----------------------------------------------------------------------------------------
\section{Summary}

@@

This was one of the largest studies involving patients who underwent cardiopulmonary exercise testing before undergoing pancreaticoduodenectomy in a tertiary specialist pancreato-biliary unit in the West of Scotland. 
The results presented here demonstrate the clinical utility of cardiopulmonary exercise testing in major pancreatic surgery in the largest cohort of patients in published literature.

The thesis also examined the effect of obstructive jaundice including severe obstructive jaundice on cardiopulmonary exercise physiology and postoperative systemic inflammation in this cohort. 
We are not aware of any other published reports on this subject.

This work also demonstrated a novel application of the trends in postoperative CRP in identifying patients at risk of infective complications which is different from the accepted paradigm for the use of postoperative CRP in published literature.

The results presented here provide the foundations for future work on prehabilitation, mitigating perioperative risks and improving outcomes after pancreaticoduodenectomy.

@@

The results presented in chapter \ref{ch_cpet_outcomes} demonstrated that cardiopulmonary exercise testing had a role in identifying high risk patients who were more likely to develop complications, stay longer in hospital and were less likely to receive adjuvant therapy after pancreaticoduodenectomy. 
These findings have since been replicated by other authors examining the role of cardiopulmonary exercise testing in pancreatic surgery.

@@

The results of our work in chapter \ref{ch_cpet_outcomes} as well as that of several others over the past two decades support the use of cardiopulmonary exercise testing as a clinical risk assessment tool in patients undergoing major surgery.

@@

%################################################################################
\subsection{Obstructive jaundice}
%################################################################################
In our opinion, the most important observation made in chapter \ref{ch_cpet_jaundice} was the lack of association between obstructive jaundice and poor cardiopulmonary function. 
We are aware of only one other similar study by Junejo and co-workers. They reported that peripheral oxygen extraction was normal during cardiopulmonary exercise in patients with malignant obstructive jaundice \parencite{junejo_peripheral_2014}.
Preoperative biliary drainage is unlikely to improve aerobic fitness or modify their cardiopulmonary response to exercise/surgery \parencite{parker_serum_2014}.

@@

In their, appropriately titled paper \textit{`The Quandary of Preresection Biliary Drainage for Pancreatic Cancer'}, the authors discuss the complex physiological effects of obstructive jaundice, its impact on immune function and the differences between findings in animal studies and humans \parencite{tol_quandary_2012}.
However, they also review recent literature where there appears to be overwhelming evidence that preoperative biliary drainage increases the incidence of postoperative complications, especially infective complications \parencite{van_der_gaag_preoperative_2010, arkadopoulos_preoperative_2014, fujii_preoperative_2015, furukawa_negative_2015}.

In chapter \ref{ch_outcomes} we reported that obstructive jaundice was not associated with increased incidence of postoperative complications or prolonged hospital stay. 
Taken together, our results support the emerging view that preoperative biliary drainage should no longer be performed routinely in all patients undergoing a pancreaticoduodenectomy unless specifically indicated such as in cholangitis.

@@

Our results suggest that poor performance at cardiopulmonary exercise testing may not necessarily be related to only cardiac or pulmonary function. 
Body composition appears to not only affect aerobic capacity but also systemic inflammation.
Improvements in body composition in cancer patients are achievable through nutritional supplementation \parencite{machado_whey_2015} as well as increased physical activity.
Perioperative nutritional supplementation has been reported to be associated with reduced postoperative complications and improved outcomes \parencite{kabata_preoperative_2015, zhang_perioperative_2012}.
